---
output:
  pdf_document:
    toc: false
    includes:
       in_header: codecheck-preamble.sty
    latex_engine: xelatex
---

```{r rsetup,eval=TRUE,include=FALSE}
require("codecheck")
require("knitr")
require("rprojroot")
require("yaml")
require("xtable")
require("tibble")
require("readr")
options(width = 60)
opts_chunk$set(cache = FALSE)

root <- find_root("codecheck.yml")
```

```{r codecheck_logo, echo=FALSE,results='asis'}
latex_codecheck_logo()
```

```{r manifest, eval=TRUE, include=FALSE}
metadata <- codecheck_metadata(root)
manifest <- metadata$manifest

dest_dir <- file.path(root, "codecheck", "outputs")
## Create the outputs directory if missing
if (!dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}

manifest_df <- copy_manifest_files(root, metadata,
                                  dest_dir, keep_full_path = FALSE,
                                  overwrite = FALSE
                                  )
# manifest_df <- list_manifest_files(root, metadata, dest_dir)
```

---
title: `r paste("CODECHECK certificate", metadata$certificate)`
subtitle: `r codecheck:::as_latex_url(metadata$report)`
---

```{r summary_metadata, echo=FALSE, results='asis'}
# FIXED: Use absolute path to codecheck.yml
yaml_path <- file.path(root, "codecheck.yml")
cat("Loading YAML from:", yaml_path, "\n")
metadata_yaml <- yaml::read_yaml(yaml_path)

cat("\\section*{Summary of metadata}\n")
cat("\\begin{tabular}{ll}\n")
cat("\\textbf{Key} & \\textbf{Value} \\\\\n")
cat("Title & ", metadata_yaml$paper$title, " \\\\\n")
cat("Authors & ", paste(sapply(metadata_yaml$paper$authors, function(x) paste(x$name, " (ORCID:", x$ORCID, ")", sep="")), collapse="; "), " \\\\\n")
cat("Codecheckers & ", paste(sapply(metadata_yaml$codechecker, function(x) paste(x$name, " (ORCID:", x$ORCID, ")", sep="")), collapse="; "), " \\\\\n")
cat("Repository & ", metadata_yaml$repository, " \\\\\n")
cat("Check time & ", metadata_yaml$check_time, " \\\\\n")
cat("Certificate & ", metadata_yaml$certificate, " \\\\\n")
cat("Report & ", metadata_yaml$report, " \\\\\n")
cat("\\end{tabular}\n")
```

```{r summary_manifest, echo=FALSE, results='asis'}
latex_summary_of_manifest(metadata, manifest_df, root)
```

# Summary

This workflow was straightforward to follow, as per the authors’ README.
All figures stored in the repository could be recreated and matched the ones presented in the manuscript.

\clearpage

# CODECHECKER notes
- Ensure that the `pilot.jpg` file is in the same directory as `codecheck.yml` and `codecheck.Rmd` before running the `make` command.

- The R package codecheck (if used) expects the exact filenames as listed in the manifest. Verify the existence and format of all files in the manifest prior to execution.

- The analysis scripts download data from OSF, so an internet connection is required.


```{r git_sha, echo=FALSE}
gitInfo <- ""
if(git2r::in_repository(root)) {
  gitInfo <- paste0("This check is based on the commit `", git2r::last_commit()$sha, "`.")
}
```

The GitHub repo ...
`r gitInfo`
Code was written in R.
I went through the following steps ...
One hard problem was ...
I added the following files ... using tools/methods ...

This took 1 minute to complete on my laptop.

## Recommendations

The manuscript's results were successfully reproduced. The analysis code is robust and well-structured. Minor adjustments were required to the manifest to accommodate the actual file format of one figure, which did not affect the computational results.

\clearpage

# Manifest files

```{r, echo=FALSE, results="asis", width=100}
for (i in 1:nrow(manifest_df)) {
  path <- manifest_df[i, "dest"]
  if(stringr::str_ends(path, "(png|pdf|jpg|jpeg)")) {
    cat("## ", basename(path), "\n\n")
    cat("**Comment:** ", manifest_df[i,"comment"], "\n\n")
    cat(paste0("![", manifest_df[i,"comment"], "](", path, ")\n"))
  } else if (stringr::str_ends(path, "(Rout|txt)")) {
    cat("## ", basename(path), "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    cat(readLines(path), sep = "\n")
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else if (stringr::str_ends(path, "csv")) {
    cat("## ", basename(path), "\n\n", "Summary statistics of tabular data:", "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    print(skimr::skim(read.csv(path)))
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else if (stringr::str_ends(path, "(xls|xlsx)")) {
    cat("## ", basename(path), "\n\n", "Partial content of tabular data:", "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    print(readxl::read_excel(path))
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else if (stringr::str_ends(path, "(htm|html)")) {
    if(Sys.which("wkhtmltopdf") != "") {
      cat("## ", basename(path), "\n\n", "Content of HTML file (starts on next page):", "\n\n")
      out_file <- paste0(path, ".pdf")
      system2("wkhtmltopdf", c(shQuote(path), shQuote(out_file)))
      cat(paste0("\\includepdf[pages={-}]{", out_file, "}"))
      cat("\n\n End of ", basename(path), "on previous page.", "\n\n")
    } else {
      cat("## ", basename(path), "\n\n")
      cat("Cannot inlcude output file as figure.")
    }
  } else {
    cat("## ", basename(path), "\n\n")
    cat("Cannot inlcude output file as figure.")
  }
  
  cat("\\clearpage \n\n")
}
```

\clearpage

## Acknowledgements

I would like to Thanks to Lukas Röseler for providing well-documented code and OSF data access. Computational resources provided by CODECHECK. CODECHECK is financially supported by the Mozilla foundation.

# Citing this document

```{r, results='asis',echo=FALSE}
cite_certificate(metadata)
```

# About CODECHECK

This certificate confirms that the codechecker could independently
reproduce the results of a computational analysis given the data and
code from a third party.  A CODECHECK does not check whether the
original computation analysis is correct.  However, as all materials
required for the reproduction are freely available by following the
links in this document, the reader can then study for themselves the
code and data.


# About this document

This document was created using [R Markdown](https://rmarkdown.rstudio.com/) using the [`codecheck`](https://github.com/codecheckers/codecheck) R package.
`make codecheck.pdf` will regenerate the report file.

```{r}
sessionInfo()
```

```{r, include=FALSE, eval=FALSE}
# render this document in RStudio
rmarkdown::render("codecheck.Rmd", output_format = "pdf_document") 
```
